%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.5in,top=0.5in,right=0.5in,bottom=0.5in]{geometry} % Document margins

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{garamondx}
\usepackage[super]{nth}

\usepackage{microtype}
\DisableLigatures{encoding = *, family = *}
\name{Angus Lim} % Your name
\address{48 9th Ave., Apt. 23A \\ New York, NY 10011} % Your address
%\address{576 W 19th Ave \\ Vancouver, BC V5Z 1W6} % Your address
\address{(206) 201-9908 \\ anguslim94@gmail.com} % Your phone number and email
%\address{(604) 872-7118 \\ anguslim94@gmail.com} % Your phone number and email

\begin{document}




%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{Google, Inc.}{06/2016 - 07/2017}{Software Engineer}{New York, NY, USA}
\item Maintained Cloud Pub/Sub, a distributed message delivery service supporting customers such as Snapchat and Spotify.
\item Designed, implemented, and rolled out features for internal components of Cloud Pub/Sub, including internal key-value stores, message storage binaries, and database adminstration tools.
\end{rSubsection}

\begin{rSubsection}{Google, Inc.}{08/2015 - 11/2015}{Software Engineer}{Mountain View, CA, USA}
\item Built a client of a Google-internal logger, exposing a simple API to first-party Android apps for simple logging of lifecycle events.
\item Integrated the client's logs into various monitors for tracking and displaying data.
\end{rSubsection}

\begin{rSubsection}{Amazon Global Resources}{09/2014 - 12/2014}{Software Development Engineer}{Seattle, WA, USA}
\item Created a Java server application to store and supply desired return values for given method signatures via HTTP.
\item Utilized AOP to enable user-defined replacement of code execution with requests to the server to retrieve data.
\end{rSubsection}

\begin{rSubsection}{Boston Pizza International}{06/2014 - 08/2014}{Learning and Technology Developer}{Richmond, BC, Canada}
\item Rewrote backend code to make use of a new MVC architecture in an upgrade of a web content management system.
\item Deployed and provided maintenance for the system upgrade on an employee training content website serving over 50000 users.
\item Optimized MySQL tables by writing and executing PHP scripts to convert XML-encoded content entries to JSON.
\end{rSubsection}

\begin{rSubsection}{JDS Uniphase Corporation}{05/2012 - 12/2012}{Digital Signal Processor (DSP) Engineer}{Vancouver, BC, Canada}
\item Designed and implemented an interface for direct communication between DSPs in an embedded system.
\item Wrote and debugged code for compiling statistics during operation of the system.
%\item Replaced arrays of buffer pools with FIFO queues, reducing internal memory usage by 22\% and external memory usage by 66\%.
\item Facilitated build server upgrades by rewriting Makefiles and code generation scripts to be compatible with new software.
\end{rSubsection}

%\begin{rSubsection}{Icron Technologies}{01/2011 - 04/2011}{Software Design Engineer}{Burnaby, BC, Canada}
%%\item Developed a Python program to communicate with proprietary hardware for testing and debugging via sockets.
%%\item Utilized the .NET Framework to create a graphical interface for the program.
%\item Developed a graphical Python program to communicate with proprietary hardware for testing and debugging via sockets.
%\item Debugged firmware and test code for hardware, using C.
%\end{rSubsection}

\end{rSection}




%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}
\begin{list}{}{\leftmargin=0em} % \cdot used for bullets, no indentation
\itemsep -0.5em % Compress items in list together for aesthetics
\item Distributed systems programming: C/C++, Python, Java
\item Unix-like (GNU/Linux, FreeBSD) operating systems and software; LAMP stack
\item Git, SVN, MATLAB/GNU Octave, LaTeX
\end{list}
\end{rSection}




%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\begin{list}{}{\leftmargin=0em} % \cdot used for bullets, no indentation
\itemsep -0.5em % Compress items in list together for aesthetics
\item {\bf University of British Columbia} \hfill 09/2009 - 05/2016
\item B.A.Sc. in Engineering Physics, Electrical Engineering stream
\end{list}

\end{rSection}




%----------------------------------------------------------------------------------------
%	RESEARCH EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Research Experience}

\begin{rSubsection}{STEMCELL Technologies}{09/2013 - 12/2013}{}{}
\item Implemented Wiener deconvolution and an iterative correction algorithm for motion deblurring of a group of images.
\item Designed a GUI with the Qt framework to apply motion deblurring to a set of microscopic images of cells.
\end{rSubsection}

\begin{rSubsection}{University of British Columbia}{01/2013 - 04/2013}{Physics \& Astronomy Department}{}
\item Implemented low-pass filters on a 32-bit microcontroller as part of a project to design a low-cost lock-in amplifier.
\item Created a GUI with PyGTK to communicate with the microcontroller via a socket and display amplitude and phase shift.
\end{rSubsection}

\begin{rSubsection}{University of British Columbia}{05/2011 - 08/2011}{Physics \& Astronomy Department}{}
\item Designed and built an autonomous robot to climb a slatted incline and a wall with a pattern of small holes.
\item Assembled and soldered H-bridge and PID controller circuits for DC motor control.
\item Wrote the software for the robot, including a state-based control system.
\end{rSubsection}

\end{rSection}




%----------------------------------------------------------------------------------------
%	EXTRACURRICULAR SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Extracurricular}

\begin{rSubsection}{ACM Pacific Northwest Regional Programming Contest}{09/2011 - 11/2015}{}{}
\item Designed, implemented, and debugged algorithms to solve given problems, while coordinating a team of three on one computer.
\item \nth{9} place (2015); \nth{11} place (2014); Canada Site Winner, \nth{4} place (2013); \nth{14} place (2012); \nth{28} place (2011)
%\item \nth{9} of 70 teams (2015); \nth{11} of 93 teams (2014); Canada Site Winner, \nth{4} of 117 teams (2013); \nth{14} of 111 teams (2012); \nth{28} of 94 teams (2011)
\end{rSubsection}

\begin{rSubsection}{Google Code Jam}{04/2012 - Present}{}{}
\item Designed, implemented, and debugged algorithms to solve given problems in online individual contests.
\item Top 1000 of over 25000 participants, Round 2 (2014)
\end{rSubsection}



%{\bf ACM Pacific Northwest Regional Programming Contest}
%\begin{list}{$\cdot$}{\leftmargin=0em} % \cdot used for bullets, no indentation
%\itemsep -0.5em \vspace{-0.5em} % Compress items in list together for aesthetics
%\item 2014/11 - \nth{11} of 93 teams
%\item 2013/11 - \nth{4} of 117 teams
%\item 2012/11 - \nth{14} of 111 teams
%\item 2011/11 - \nth{28} of 94 teams
%\end{list}
%{\bf Google Code Jam}
%\begin{list}{$\cdot$}{\leftmargin=0em} % \cdot used for bullets, no indentation
%\itemsep -0.5em \vspace{-0.5em} % Compress items in list together for aesthetics
%\item 2014/05 - Top 1000, Round 2
%\end{list}


\end{rSection}




%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
